---
title: "Materials for 'Validating daily social media macroscopes of emotions'"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE,warning=FALSE,message=FALSE,cache=FALSE)
library(data.table)
library(lubridate)
library(zoo)
library(ggplot2)
library(lmtest)
library(sandwich)
library(xtable)
library(cocor)
library(boot)

theme_thesis <- function(){
  theme_bw() %+replace%
    theme(
      #line = element_line(colour="black"),
      #text = element_text(colour="black"),
      axis.title = element_text(size = 14),
      axis.text = element_text(colour="black", size=12),
      #strip.text = element_text(size=12),
      # legend.key=element_rect(colour=NA, fill =NA),
      panel.grid.major = element_line(colour = "grey90"),
      panel.grid.minor = element_line(colour="grey90"),
      # panel.border = element_rect(fill = NA, colour = "black", size=1),
      panel.background = element_rect(fill = "white"),
      strip.background=element_rect(fill="white")#,
      #legend.title=element_blank()
      # legend.position="none"
    )
}

theme_set(theme_thesis())

Sys.setlocale("LC_ALL", 'en_US.UTF-8')

wmean <- function(x) weighted.mean(x[, 1], x[, 2])
```

# Der Standard

```{r derstandard_plots, fig.show="hold", out.width="50%"}
pl <- readRDS("pl.RDS")

# Scatterplot regression

pl <- na.omit(pl)

ggplot(pl, aes(x=sent_roll3_weighted,y=prop_good)) +
  geom_smooth(method="lm",color = "black") + geom_point() + ylab('Proportion of Positive in Survey') +
  xlab("Text Sentiment Average") + theme(axis.title = element_text(size = 18),axis.text = element_text(colour="black", size=16))


# Changes regression
# We lose one data point because we cannot compute a change on the first day of the survey

pl <- readRDS("pl.RDS")

pl$difgood <- c(NA,diff(pl$prop_good))
pl$difsent <- c(NA,diff(pl$sent_roll3_weighted))

pl <- na.omit(pl)

ggplot(pl, aes(x=difsent,y=difgood)) +
  geom_smooth(method="lm",color = "black") + geom_point() + ylab('Change of Proportion of Positive') +
  xlab("Change of Text Sentiment Average") + geom_vline(xintercept =0,linetype=2) +
  geom_hline(yintercept =0,linetype=2) + theme(axis.title = element_text(size = 18),axis.text = element_text(colour="black", size=16))

```

## Scatterplot regression and correlation
```{r}
pl <- readRDS("pl.RDS")

pl <- na.omit(pl)

fit_scatter <- lm(prop_good ~ sent_roll3_weighted,data=pl)

summary(fit_scatter)

cor.test(pl$prop_good,pl$sent_roll3_weighted)
```

## Scatterplot test of coefficients
```{r}
round(coeftest(fit_scatter, vcov=vcovHAC(fit_scatter)),3)

round(coefci(fit_scatter, vcov=vcovHAC(fit_scatter)),3)
```

## Differences regression and correlation
```{r}
pl <- readRDS("pl.RDS")

pl$difgood <- c(NA,diff(pl$prop_good))
pl$difsent <- c(NA,diff(pl$sent_roll3_weighted))

pl <- na.omit(pl)

fit_change <- lm(difgood ~ difsent,pl)

summary(fit_change)

cor.test(pl$difgood,pl$difsent)
```

## Differences test of coefficients
```{r}
round(coeftest(fit_change, vcov=vcovHAC(fit_change)),3)

round(coefci(fit_change, vcov=vcovHAC(fit_change)),3)
```

## Side by side plot

```{r}
pl <- readRDS("pl.RDS")

pl <- na.omit(pl)

pl[,date_day:=date]

mp <- lm(prop_good~sent_roll3_weighted,data=pl)

blcis_twitter <- readRDS("boot_survey_twitter.RDS")

cidt <- data.table(matrix(unlist(blcis_twitter),ncol=2,byrow=T))

setnames(cidt,c("cimin","cimax"))

ggplot(cbind(pl,cidt), aes(x=date_day)) +
  geom_line( aes(y=prop_good),size=1.1,color="blue") +
  geom_line( aes(y=mp$coefficients[1] + mp$coefficients[2]*sent_roll3_weighted), color="red",size=1.1) +
  scale_y_continuous(
    name = '% Positive Emotions in Survey',
    sec.axis = sec_axis(~mp$coefficients[1] + mp$coefficients[2]*., name="Der Standard Text Sentiment")
  ) + theme_thesis() + theme(axis.line.y.right = element_line(color = "red"),
                             axis.ticks.y.right = element_line(color = "red"), axis.title.y.right = element_text(color = "red")) + xlab("Date") + geom_point(aes(y=prop_good)) + geom_point(aes(y=mp$coefficients[1] + mp$coefficients[2]*sent_roll3_weighted),color="red") + geom_ribbon(aes(y=prop_good,ymin=cimin,ymax=cimax),alpha=0.25, bg="blue")
```


# Twitter

```{r twitter_plots, fig.show="hold", out.width="50%"}
cdplstandard <- readRDS("cdplstandard.RDS")

# Scatterplot regression

cdplstandard <- na.omit(cdplstandard)

ggplot(cdplstandard, aes(x=sent_roll3_weighted_shifted1,y=prop_good)) +
  geom_smooth(method="lm",color = "black") + geom_point() + ylab('Proportion of Positive in Survey') +
  xlab("Text Sentiment Average") + theme(axis.title = element_text(size = 18),axis.text = element_text(colour="black", size=16))


# Changes regression
# Again, we lose one data point because we cannot compute a change on the first day of the survey

cdplstandard <- readRDS("cdplstandard.RDS")

cdplstandard$difgood <- c(NA,diff(cdplstandard$prop_good))
cdplstandard$difsent <- c(NA,diff(cdplstandard$sent_roll3_weighted_shifted1))

cdplstandard <- na.omit(cdplstandard)

ggplot(cdplstandard, aes(x=difsent,y=difgood)) +
  geom_smooth(method="lm",color = "black") + geom_point() + ylab('Change of Proportion of Positive') +
  xlab("Change of Text Sentiment Average") + geom_vline(xintercept =0,linetype=2) +
  geom_hline(yintercept =0,linetype=2) + theme(axis.title = element_text(size = 18),axis.text = element_text(colour="black", size=16))

```

## Scatterplot regression and correlation
```{r}
cdplstandard <- readRDS("cdplstandard.RDS")

cdplstandard <- na.omit(cdplstandard)

fit_scatter <- lm(prop_good ~ sent_roll3_weighted_shifted1,data=cdplstandard)

summary(fit_scatter)

cor.test(cdplstandard$prop_good,cdplstandard$sent_roll3_weighted_shifted1)
```

## Scatterplot test of coefficients
```{r}
round(coeftest(fit_scatter, vcov=vcovHAC(fit_scatter)),3)

round(coefci(fit_scatter, vcov=vcovHAC(fit_scatter)),3)
```

## Differences regression and correlation
```{r}
cdplstandard <- readRDS("cdplstandard.RDS")

cdplstandard$difgood <- c(NA,diff(cdplstandard$prop_good))
cdplstandard$difsent <- c(NA,diff(cdplstandard$sent_roll3_weighted_shifted1))

cdplstandard <- na.omit(cdplstandard)

fit_change <- lm(difgood ~ difsent,cdplstandard)

summary(fit_change)

cor.test(cdplstandard$difgood,cdplstandard$difsent)
```

## Differences test of coefficients
```{r}
round(coeftest(fit_change, vcov=vcovHAC(fit_change)),3)

round(coefci(fit_change, vcov=vcovHAC(fit_change)),3)
```

## Side by side plot

```{r}
cdplstandard <- readRDS("cdplstandard.RDS")

cdplstandard <- na.omit(cdplstandard)

mp <- lm(prop_good~sent_roll3_weighted_shifted1,data=cdplstandard)

blcis_twitter <- readRDS("boot_survey_twitter.RDS")

cidt <- data.table(matrix(unlist(blcis_twitter),ncol=2,byrow=T))

setnames(cidt,c("cimin","cimax"))

ggplot(cbind(cdplstandard,cidt), aes(x=date_day)) +
  geom_line( aes(y=prop_good),size=1.1,color="blue") +
  geom_line( aes(y=mp$coefficients[1] + mp$coefficients[2]*sent_roll3_weighted_shifted1), color="red",size=1.1) +
  scale_y_continuous(
    name = '% Positive Emotions in Survey',
    sec.axis = sec_axis(~mp$coefficients[1] + mp$coefficients[2]*., name="Twitter Text Sentiment")
  ) + theme_thesis() + theme(axis.line.y.right = element_line(color = "red"),
                             axis.ticks.y.right = element_line(color = "red"), axis.title.y.right = element_text(color = "red")) + xlab("Date") + geom_point(aes(y=prop_good)) + geom_point(aes(y=mp$coefficients[1] + mp$coefficients[2]*sent_roll3_weighted_shifted1),color="red") + geom_ribbon(aes(y=prop_good,ymin=cimin,ymax=cimax),alpha=0.25, bg="blue")
```

# Twitter Pre-Registration Correlations

## Exactly like in Pre-Registration

```{r}
# exactly like in prereg
cdplstandard_prereg <- readRDS("cdplstandard_prereg.RDS")

round(cor(na.omit(cdplstandard_prereg)$sent_roll3_weighted,na.omit(cdplstandard_prereg)$prop_good),2)

paste0("[",paste0(round(cor.test(cdplstandard_prereg$prop_good,cdplstandard_prereg$sent_roll3_weighted)$conf.int,2),collapse=","),"]")

round(cor.test(cdplstandard_prereg$prop_good,cdplstandard_prereg$sent_roll3_weighted)$p.value,4)
```

## Change to follower limit of 100 000

```{r}
cdplstandard <- readRDS("cdplstandard.RDS")

round(cor(na.omit(cdplstandard)$sent_roll3_weighted,na.omit(cdplstandard)$prop_good),2)

paste0("[",paste0(round(cor.test(cdplstandard$prop_good,cdplstandard$sent_roll3_weighted)$conf.int,2),collapse=","),"]")

round(cor.test(cdplstandard$prop_good,cdplstandard$sent_roll3_weighted)$p.value,5)
```


# Twitter Shifts

```{r twitter_shifts, fig.show="hold", out.width="50%"}
cdplstandard <- readRDS("cdplstandard.RDS")

cdplstandard <- na.omit(cdplstandard)

# without shift

mp_without <- lm(prop_good~sent_roll3_weighted,data=cdplstandard)

blcis_twitter <- readRDS("boot_survey_twitter.RDS")

cidt <- data.table(matrix(unlist(blcis_twitter),ncol=2,byrow=T))

setnames(cidt,c("cimin","cimax"))

ggplot(cbind(cdplstandard[date_day>=as.Date("2020-11-11")],cidt), aes(x=date_day)) +
  geom_line( aes(y=prop_good),size=1.1,color="blue") +
  geom_line( aes(y=mp_without$coefficients[1] + mp_without$coefficients[2]*sent_roll3_weighted), color="red",size=1.1) +
  scale_y_continuous(
    name = '% Positive Emotions in Survey',
    sec.axis = sec_axis(~mp_without$coefficients[1] + mp_without$coefficients[2]*., name="Text Sentiment")
  ) + theme_thesis() + theme(axis.line.y.right = element_line(color = "red"),
                             axis.ticks.y.right = element_line(color = "red"), axis.title.y.right = element_text(color = "red")) + xlab("Date") + geom_point(aes(y=prop_good)) + geom_point(aes(y=mp_without$coefficients[1] + mp_without$coefficients[2]*sent_roll3_weighted),color="red") + geom_ribbon(aes(y=prop_good,ymin=cimin,ymax=cimax),alpha=0.25, bg="blue") +
  ggtitle("No Shift")


# shifted1

mp_shifted1 <- lm(prop_good~sent_roll3_weighted_shifted1,data=cdplstandard)

ggplot(cbind(cdplstandard[date_day>=as.Date("2020-11-11")],cidt), aes(x=date_day)) +
  geom_line( aes(y=prop_good),size=1.1,color="blue") +
  geom_line( aes(y=mp_shifted1$coefficients[1] + mp_shifted1$coefficients[2]*sent_roll3_weighted_shifted1), color="red",size=1.1) +
  scale_y_continuous(
    name = '% Positive Emotions in Survey',
    sec.axis = sec_axis(~mp_shifted1$coefficients[1] + mp_shifted1$coefficients[2]*., name="Text Sentiment")
  ) + theme_thesis() + theme(axis.line.y.right = element_line(color = "red"),
                             axis.ticks.y.right = element_line(color = "red"), axis.title.y.right = element_text(color = "red")) + xlab("Date") + geom_point(aes(y=prop_good)) + geom_point(aes(y=mp_shifted1$coefficients[1] + mp_shifted1$coefficients[2]*sent_roll3_weighted_shifted1),color="red") + geom_ribbon(aes(y=prop_good,ymin=cimin,ymax=cimax),alpha=0.25, bg="blue") +
  ggtitle("Shift 1")
```

# Tables

```{r corrtable_comparison, results='asis'}
twtable <- c(cor(cdplstandard$prop_good,cdplstandard$sent_roll3_weighted_shifted1),
             cor(cdplstandard$prop_good,cdplstandard$sentA_roll3_weighted_shifted1),
             cor(cdplstandard$prop_good,cdplstandard$sentA_pos_roll3_weighted_shifted1),
             cor(cdplstandard$prop_good,cdplstandard$sentA_neg_roll3_weighted_shifted1),
             cor(cdplstandard$prop_good,cdplstandard$sentB_roll3_weighted_shifted1),
             cor(cdplstandard$prop_good,cdplstandard$sentB_pos_roll3_weighted_shifted1),
             cor(cdplstandard$prop_good,cdplstandard$sentB_neg_roll3_weighted_shifted1))

twtableconfint <- c(paste0("[",paste0(round(cor.test(cdplstandard$prop_good,cdplstandard$sent_roll3_weighted_shifted1)$conf.int,2),collapse=","),"]"),
                    paste0("[",paste0(round(cor.test(cdplstandard$prop_good,cdplstandard$sentA_roll3_weighted_shifted1)$conf.int,2),collapse=","),"]"),
                    paste0("[",paste0(round(cor.test(cdplstandard$prop_good,cdplstandard$sentA_pos_roll3_weighted_shifted1)$conf.int,2),collapse=","),"]"),
                    paste0("[",paste0(round(cor.test(cdplstandard$prop_good,cdplstandard$sentA_neg_roll3_weighted_shifted1)$conf.int,2),collapse=","),"]"),
                    paste0("[",paste0(round(cor.test(cdplstandard$prop_good,cdplstandard$sentB_roll3_weighted_shifted1)$conf.int,2),collapse=","),"]"),
                    paste0("[",paste0(round(cor.test(cdplstandard$prop_good,cdplstandard$sentB_pos_roll3_weighted_shifted1)$conf.int,2),collapse=","),"]"),
                    paste0("[",paste0(round(cor.test(cdplstandard$prop_good,cdplstandard$sentB_neg_roll3_weighted_shifted1)$conf.int,2),collapse=","),"]"))
                    

twtable_names_overall_nice <- c("LIWC+GS","LIWC","LIWC pos","LIWC neg","GS","GS pos","GS neg")


# table Twitter no shift

twtable_noshift <- c(cor(cdplstandard$prop_good,cdplstandard$sent_roll3_weighted),
             cor(cdplstandard$prop_good,cdplstandard$sentA_roll3_weighted),
             cor(cdplstandard$prop_good,cdplstandard$sentA_pos_roll3_weighted),
             cor(cdplstandard$prop_good,cdplstandard$sentA_neg_roll3_weighted),
             cor(cdplstandard$prop_good,cdplstandard$sentB_roll3_weighted),
             cor(cdplstandard$prop_good,cdplstandard$sentB_pos_roll3_weighted),
             cor(cdplstandard$prop_good,cdplstandard$sentB_neg_roll3_weighted))

twtableconfint_noshift <- c(paste0("[",paste0(round(cor.test(cdplstandard$prop_good,cdplstandard$sent_roll3_weighted)$conf.int,2),collapse=","),"]"),
                    paste0("[",paste0(round(cor.test(cdplstandard$prop_good,cdplstandard$sentA_roll3_weighted)$conf.int,2),collapse=","),"]"),
                    paste0("[",paste0(round(cor.test(cdplstandard$prop_good,cdplstandard$sentA_pos_roll3_weighted)$conf.int,2),collapse=","),"]"),
                    paste0("[",paste0(round(cor.test(cdplstandard$prop_good,cdplstandard$sentA_neg_roll3_weighted)$conf.int,2),collapse=","),"]"),
                    paste0("[",paste0(round(cor.test(cdplstandard$prop_good,cdplstandard$sentB_roll3_weighted)$conf.int,2),collapse=","),"]"),
                    paste0("[",paste0(round(cor.test(cdplstandard$prop_good,cdplstandard$sentB_pos_roll3_weighted)$conf.int,2),collapse=","),"]"),
                    paste0("[",paste0(round(cor.test(cdplstandard$prop_good,cdplstandard$sentB_neg_roll3_weighted)$conf.int,2),collapse=","),"]"))


dtable <- c(cor(pl$prop_good,pl$sent_roll3_weighted),
            cor(pl$prop_good,pl$sentA_roll3_weighted),
            cor(pl$prop_good,pl$sentA_pos_roll3_weighted),
            cor(pl$prop_good,pl$sentA_neg_roll3_weighted),
            cor(pl$prop_good,pl$sentB_roll3_weighted),
            cor(pl$prop_good,pl$sentB_pos_roll3_weighted),
            cor(pl$prop_good,pl$sentB_neg_roll3_weighted))


dtableconfint <- c(paste0("[",paste0(round(cor.test(pl$prop_good,pl$sent_roll3_weighted)$conf.int,2),collapse=","),"]"),
                    paste0("[",paste0(round(cor.test(pl$prop_good,pl$sentA_roll3_weighted)$conf.int,2),collapse=","),"]"),
                    paste0("[",paste0(round(cor.test(pl$prop_good,pl$sentA_pos_roll3_weighted)$conf.int,2),collapse=","),"]"),
                    paste0("[",paste0(round(cor.test(pl$prop_good,pl$sentA_neg_roll3_weighted)$conf.int,2),collapse=","),"]"),
                    paste0("[",paste0(round(cor.test(pl$prop_good,pl$sentB_roll3_weighted)$conf.int,2),collapse=","),"]"),
                    paste0("[",paste0(round(cor.test(pl$prop_good,pl$sentB_pos_roll3_weighted)$conf.int,2),collapse=","),"]"),
                    paste0("[",paste0(round(cor.test(pl$prop_good,pl$sentB_neg_roll3_weighted)$conf.int,2),collapse=","),"]"))


# build table

tabledt <- data.frame(paste(sprintf("%.2f",round(dtable,2)),dtableconfint),paste(sprintf("%.2f",round(twtable,2)),twtableconfint),paste(sprintf("%.2f",round(twtable_noshift,2)),twtableconfint_noshift))

colnames(tabledt) <- c("derstandard","Twitter (Shift 1)","Twitter (No Shift)")

rownames(tabledt) <- twtable_names_overall_nice

print(xtable(tabledt),comment=F)
```

```{r table_cordifferences,results='asis'}
cdplstandard <- readRDS("cdplstandard.RDS")

cdplstandard <- na.omit(cdplstandard)


pl <- readRDS("/home/maxpe/derstandard_decanalysis/pl.RDS")

pl[,date_day:=date]

pl <- na.omit(pl)


plselect <- c("date_day","sent_roll3_weighted","sentA_roll3_weighted","sentB_roll3_weighted","sentA_pos_roll3_weighted","sentA_neg_roll3_weighted","sentB_pos_roll3_weighted","sentB_neg_roll3_weighted")

plselectdt <- pl[,.SD,.SDcols=plselect]

setnames(plselectdt,plselect[-1],paste0(plselect[-1],"_derstandard"))


cdplselect <- c("prop_good","date_day","sent_roll3_weighted_shifted1","sentA_roll3_weighted_shifted1","sentB_roll3_weighted_shifted1","sentA_pos_roll3_weighted_shifted1","sentA_neg_roll3_weighted_shifted1","sentB_pos_roll3_weighted_shifted1","sentB_neg_roll3_weighted_shifted1")

cdplselectdt <- cdplstandard[,.SD,.SDcols=cdplselect]

setnames(cdplselectdt,cdplselect[-c(1,2)],paste0(cdplselect[-c(1,2)],"_twitter"))

# Corrrelation comparison
# Method is hittner2003

cordt <- merge(plselectdt,cdplselectdt,by="date_day")

# reverse negative
cordt[,sentA_neg_roll3_weighted_derstandard_reversed:=1-sentA_neg_roll3_weighted_derstandard]

cordt[,sentB_neg_roll3_weighted_derstandard_reversed:=1-sentB_neg_roll3_weighted_derstandard]


cordt[,sentA_neg_roll3_weighted_shifted1_twitter_reversed:=1-sentA_neg_roll3_weighted_shifted1_twitter]

cordt[,sentB_neg_roll3_weighted_shifted1_twitter_reversed:=1-sentB_neg_roll3_weighted_shifted1_twitter]

# reversed
twtable <- c(cocor(~prop_good + sent_roll3_weighted_derstandard|prop_good + sent_roll3_weighted_shifted1_twitter,data=cordt)@hittner2003$p.value,
             cocor(~prop_good + sentA_roll3_weighted_derstandard|prop_good + sentB_roll3_weighted_derstandard,data=cordt)@hittner2003$p.value,
             cocor(~prop_good + sentA_roll3_weighted_shifted1_twitter|prop_good + sentB_roll3_weighted_shifted1_twitter,data=cordt)@hittner2003$p.value,
             cocor(~prop_good + sentA_pos_roll3_weighted_derstandard|prop_good + sentA_neg_roll3_weighted_derstandard_reversed,data=cordt)@hittner2003$p.value,
             cocor(~prop_good + sentA_pos_roll3_weighted_shifted1_twitter|prop_good + sentA_neg_roll3_weighted_shifted1_twitter_reversed,data=cordt)@hittner2003$p.value,
             cocor(~prop_good + sentB_pos_roll3_weighted_derstandard|prop_good + sentB_neg_roll3_weighted_derstandard_reversed,data=cordt)@hittner2003$p.value,
             cocor(~prop_good + sentB_pos_roll3_weighted_shifted1_twitter|prop_good + sentB_neg_roll3_weighted_shifted1_twitter_reversed,data=cordt)@hittner2003$p.value)

# absolute
twtable_diff <- c(abs(cor(cordt$prop_good,cordt$sent_roll3_weighted_derstandard)) - abs(cor(cordt$prop_good,cordt$sent_roll3_weighted_shifted1_twitter)),
abs(cor(cordt$prop_good,cordt$sentB_roll3_weighted_derstandard))-abs(cor(cordt$prop_good,cordt$sentA_roll3_weighted_derstandard)),
abs(cor(cordt$prop_good,cordt$sentB_roll3_weighted_shifted1_twitter)) - abs(cor(cordt$prop_good,cordt$sentA_roll3_weighted_shifted1_twitter)),
abs(cor(cordt$prop_good,cordt$sentA_pos_roll3_weighted_derstandard)) - abs(cor(cordt$prop_good,cordt$sentA_neg_roll3_weighted_derstandard)),
abs(cor(cordt$prop_good,cordt$sentA_pos_roll3_weighted_shifted1_twitter)) - abs(cor(cordt$prop_good,cordt$sentA_neg_roll3_weighted_shifted1_twitter)),
abs(cor(cordt$prop_good,cordt$sentB_pos_roll3_weighted_derstandard)) - abs(cor(cordt$prop_good,cordt$sentB_neg_roll3_weighted_derstandard)),
abs(cor(cordt$prop_good,cordt$sentB_pos_roll3_weighted_shifted1_twitter)) - abs(cor(cordt$prop_good,cordt$sentB_neg_roll3_weighted_shifted1_twitter)))

twtable_diff_names <- paste(round(twtable_diff,2),c("(Der Standard)","(GS)","(GS)","(LIWC pos)","(LIWC pos)","(GS pos)","(GS pos)"))

twtable_names <- c("Twitter vs Der Standard (Aggregate Sentiment)","GS vs. LIWC (Der Standard)","GS vs. LIWC (Twitter)","LIWC neg vs. LIWC pos (Der Standard)","LIWC neg vs. LIWC pos (Twitter)","GS neg vs. GS pos (Der Standard)","GS neg vs. GS pos (Twitter)")

tabledt <- data.frame(round(twtable,8),twtable_diff_names)

colnames(tabledt) <- c("p Value","Absolute difference")

rownames(tabledt) <- twtable_names

print(xtable(tabledt,digits=7),comment=F)
```

# Evaluation with COVID-19 cases

```{r,results='asis'}
covs <- readRDS("covs.RDS")

# twitter data
cdplstandard <- readRDS("cdplstandard.RDS")

# derstandard postings
pl <- readRDS("pl.RDS")

cdplstandard <- merge(cdplstandard,covs,by="date_day")

pl[,date_day:=date]

tdt <- na.omit(merge(pl[,.(date_day,sent_roll3_weighted,prop_good)],cdplstandard[,.(date_day,sent_roll3_weighted_twitter=sent_roll3_weighted,sent_roll3_weighted_shifted1_twitter=sent_roll3_weighted_shifted1)],by="date_day"))

covs[,diff_new_cases:=c(NA,diff(new_cases))]

tdtcovs <- merge(tdt,covs,by="date_day")

dtable <- c(cor(tdtcovs$sent_roll3_weighted_shifted1_twitter,tdtcovs$new_cases),
            cor(tdtcovs$sent_roll3_weighted_twitter,tdtcovs$new_cases),
            cor(tdtcovs$prop_good,tdtcovs$new_cases),
            cor(tdtcovs$sent_roll3_weighted,tdtcovs$new_cases))


dtableconfint <- c(paste0("[",paste0(round(cor.test(tdtcovs$sent_roll3_weighted_shifted1_twitter,tdtcovs$new_cases)$conf.int,2),collapse=","),"]"),
                   paste0("[",paste0(round(cor.test(tdtcovs$sent_roll3_weighted_twitter,tdtcovs$new_cases)$conf.int,2),collapse=","),"]"),
                   paste0("[",paste0(round(cor.test(tdtcovs$prop_good,tdtcovs$new_cases)$conf.int,2),collapse=","),"]"),
                   paste0("[",paste0(round(cor.test(tdtcovs$sent_roll3_weighted,tdtcovs$new_cases)$conf.int,2),collapse=","),"]"))


dtable_names <- c("Twitter (Aggregate Shift 1)","Twitter (Aggregate No Shift)","Survey","Der Standard (Aggregate)")

tabledt <- data.frame(paste(sprintf("%.2f",round(dtable,2)),dtableconfint))

colnames(tabledt) <- c("New Cases")

rownames(tabledt) <- dtable_names

print(xtable(tabledt),comment=F)
```

```{r,results='asis'}
cordt <- merge(cordt,covs,all.x=T,by="date_day")

twtable <- c(cocor(~new_cases + sent_roll3_weighted_shifted1_twitter|new_cases + prop_good,data=cordt)@hittner2003$p.value,
             cocor(~new_cases + sentA_roll3_weighted_shifted1_twitter|new_cases + prop_good,data=cordt)@hittner2003$p.value,
             cocor(~new_cases + sentB_roll3_weighted_shifted1_twitter|new_cases + prop_good,data=cordt)@hittner2003$p.value,
             cocor(~new_cases + sent_roll3_weighted_derstandard|new_cases + prop_good,data=cordt)@hittner2003$p.value,
             cocor(~new_cases + sentA_roll3_weighted_derstandard|new_cases + prop_good,data=cordt)@hittner2003$p.value,
             cocor(~new_cases + sentB_roll3_weighted_derstandard|new_cases + prop_good,data=cordt)@hittner2003$p.value)

twtable_diff <- c(cor(cordt$prop_good,cordt$new_cases) - cor(cordt$new_cases,cordt$sent_roll3_weighted_shifted1_twitter),
                  cor(cordt$prop_good,cordt$new_cases)-cor(cordt$new_cases,cordt$sentA_roll3_weighted_shifted1_twitter),
                  cor(cordt$prop_good,cordt$new_cases) - cor(cordt$new_cases,cordt$sentB_roll3_weighted_shifted1_twitter),
                  cor(cordt$prop_good,cordt$new_cases) - cor(cordt$new_cases,cordt$sent_roll3_weighted_derstandard),
                  cor(cordt$prop_good,cordt$new_cases) - cor(cordt$new_cases,cordt$sentA_roll3_weighted_derstandard),
                  cor(cordt$prop_good,cordt$new_cases) - cor(cordt$new_cases,cordt$sentB_roll3_weighted_derstandard))

twtable_diff_names <- paste(round(twtable_diff,2),c("(Twitter)","(Twitter LIWC)","(Twitter GS)","(Survey)","(Survey)","(Survey)"))


twtable_names <- c("Twitter (Aggregate Sentiment) vs. Survey","Twitter (LIWC) vs. Survey","Twitter (GS) vs. Survey","derstandard (Aggregate Sentiment) vs. Survey","derstandard (LIWC) vs. Survey","derstandard (GS) vs. Survey")
tabledt <- data.frame(round(twtable,8),twtable_diff_names)

colnames(tabledt) <- c("p Value","Difference (higher)")

rownames(tabledt) <- twtable_names

print(xtable(tabledt,digits=3),comment=F)
```

## Scatterplots COVID-19 cases

```{r scatter_cases,fig.show="hold", out.width="50%"}
pl[,date_day:=date]

tdt <- na.omit(merge(pl[,.(date_day,sent_roll3_weighted,prop_good)],cdplstandard[,.(date_day,sent_roll3_weighted_twitter=sent_roll3_weighted,sent_roll3_weighted_shifted1_twitter=sent_roll3_weighted_shifted1)],by="date_day"))

covs[,diff_new_cases:=c(NA,diff(new_cases))]

tdtcovs <- merge(tdt,covs,by="date_day")

# scatterplots with new cases

ggplot(tdtcovs,aes(x=sent_roll3_weighted_shifted1_twitter,y=new_cases)) + geom_point() + geom_smooth(method="lm",color="dark grey",alpha=0.5,se=F) + ylab("New COVID-19 Cases") + xlab("Aggregate Text Sentiment (Twitter Shift 1)")

ggplot(tdtcovs,aes(x=sent_roll3_weighted_twitter,y=new_cases)) + geom_point() + geom_smooth(method="lm",color="dark grey",alpha=0.5,se=F) + ylab("New COVID-19 Cases") + xlab("Aggregate Text Sentiment (Twitter)")

ggplot(tdtcovs,aes(x=prop_good,y=new_cases)) + geom_point() + geom_smooth(method="lm",color="dark grey",alpha=0.5,se=F) + ylab("New COVID-19 Cases") + xlab("Proportion of Positive in Survey")

ggplot(tdtcovs,aes(x=sent_roll3_weighted,y=new_cases)) + geom_point() + geom_smooth(method="lm",color="dark grey",alpha=0.5,se=F) + ylab("New COVID-19 Cases") + xlab("Aggregate Text Sentiment (derstandard)")
```


# Bootstraping

```{r bootstrap_plots,fig.show="hold", out.width="50%",eval=F}
#This is not evaluated by default to save time for knitting
#If you want to run it, set the number of cores that are available in the boot function

bootcortestfn <- function(first,second){
  
  cordt <- cordt[,.SD,.SDcols=c(first,second,"prop_good")]
  
  corcompare_diff <- function(data,indices){
    s <- data[indices]
    cor1 <- cor(s[[1]],s$prop_good)
    cor2 <- cor(s[[2]],s$prop_good)
    return(cor2-cor1)
  }
  
  cors <- boot(cordt,corcompare_diff,R=100000,parallel="multicore",ncpus=4)
}

bootlist <- list(list("sent_roll3_weighted_derstandard","sent_roll3_weighted_shifted1_twitter"),
list("sentB_roll3_weighted_derstandard","sentA_roll3_weighted_derstandard"),
list("sentB_roll3_weighted_shifted1_twitter","sentA_roll3_weighted_shifted1_twitter"),
list("sentA_pos_roll3_weighted_derstandard","sentA_neg_roll3_weighted_derstandard"),
list("sentA_pos_roll3_weighted_shifted1_twitter","sentA_neg_roll3_weighted_shifted1_twitter"),
list("sentB_pos_roll3_weighted_derstandard","sentB_neg_roll3_weighted_derstandard"),
list("sentB_pos_roll3_weighted_shifted1_twitter","sentB_neg_roll3_weighted_shifted1_twitter"))

# Plot Loop
twtable_names <- c("Twitter vs derstandard (aggregate Sentiment)","GS vs. LIWC (derstandard)","GS vs. LIWC (Twitter)","LIWC neg vs. LIWC pos (derstandard)","LIWC neg vs. LIWC pos (Twitter)","GS neg vs. GS pos (derstandard)","GS neg vs. GS pos (Twitter)")

for (i in 1:length(bootlist)){
cors <- bootcortestfn(bootlist[[i]][[1]],bootlist[[i]][[2]])

apply(cors$t,2, quantile, c(.025, 0.975),na.rm=T)[,1]

corsdt <- as.data.table(cors$t)

setnames(corsdt,"t")

d <- density(corsdt$t)

print(ggplot(corsdt,aes(x=t)) + geom_density(fill="red") + ggtitle(twtable_names[i]) + annotate("text",label=paste0('95% CI\n [',paste0(round(apply(cors$t,2, quantile, c(.025, 0.975),na.rm=T)[,1],2),collapse = ","),']'),x = max(d$x)-(max(d$x)*0.1), y = max(d$y)- (max(d$y)*0.1)) + scale_x_continuous(limits = c(-2, 0.5)))
}
```

